%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

\usepackage{blindtext} % Package to generate dummy text throughout this template 

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{RNN-Coin $\bullet$ November 2017} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{RNN-Coin} % Article title
\author{%
\textsc{Recurrent N. Network} \\[1ex] % Your name
% \normalsize \href{mailto:smithclay@gmail.com}{smithclay@gmail.com} % Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent A purely peer-to-peer version of the company system with the price of the system to develop and the contract agent servers and the price of the system of the system which is a simple decentralized system which is the contract to provide the contract and the structure of the system will be able to provide a service system that allows the contract agent servers with the system as a result of the project's wallet that are committed to the contract agent services that allow the development of the system will be developed by the contract and the structure of the system will be able to control other payments on the contract agent services and the contract is a simple proof of the system that allows the contract is a secure of the contract and the application can be considered as a result of the blockchain.% Dummy abstract text - replace \blindtext with your abstract text
\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}

\lettrine[nindent=0em,lines=3]{W}e define an electronic coin as a chain of the system where the first phase of the contract is a secure activity to the contract agent servers to provide a second statistical project's common and the contract is a protocol of the contract and the contract is the static between the price of the service of the contract and the app that is complicated to the project of the system where the contract is a secure of the contract and increase the price of the system which are stated by the contract agent to the project.
%------------------------------------------------

\section{The local revolution of experience}

The local revolution of experience with the results of the funds in which contracts to the organization will be reputational. The ACTs monetize the fragment price is a security and share and based on the average foundation to the blockchain technology end to be entered to the advertising results of transactions.

The project's price of the system will be able to control other content and security and support to start the contract and the system will be able to provide a service that is a secure minting price of the system will be an open manner. The average weighted transaction is the static of the community.

%------------------------------------------------

\section{Legal Proofs of Games and Projects}

It is required to even more people and use the project for real dividends of storage and legal proofs of games and projects into the following exchange of a decentralized event's commitment in the best positive and deposit the first revenue of the core team can be constructed for the project's proof. 

The advantage of the price of the blockchain technology by a development of individual and security and simply a same time that the context of cryptocurrencies are better analytical review to another sending of an asset of the hub cryptocurrency to be released in a blockchain and the development of the system that expect the contract and the legal team believes that the rent solution will be bound to the project rate of a contract as a service of all of the community.

%------------------------------------------------

\section{Transaction Cost}

The transaction cost in the core teams account with a secure decentralized state of the highest community websites and interesting the user experience on the Tezos token balance for an intelligent agent to progress any scale to make content and such as such as following the community.

%------------------------------------------------

\section{Set of Security for Regulatory Security}

This is a separate product and extend the original point and design a failure of a security of funds and start to leverage services with the price of BTC or tokens in the first ICO is the set of security and for regulatory security ensuring the data owner may include the statistical platform that operates a smart contract agent can be established to be expected with the company that is a single explored solution to the Purchaser and financial and increasing the contract participation will be sent to the lessee agents and the status market will be developed by the contract while make in a trust decentralized amount of game contracts, but the ability to participate in the stream of providing contracts and market.

%------------------------------------------------

\section{High Commitment Wallets}

This is the highest commitment wallet that a confident of money for medical currencies of the project in the initiative instruments of the project is the farmer of the cost of the system. There are not any positive to real world use the state of the transaction in the system to be interested in the contract to provide a particular time of a payment market that is purchasing in the event that the transaction contains funding between the transaction could be used to be determined by the ongoing process of the system is an entrepreneur and manage the first more information about a token crowd into the transaction value between a special transaction community communication for the crowdsale. 

If the crowdfunding between control of the system may be used to retrieve the exchange of contract and may be authorized to a large number of payments such as strong of the following system as well as the social media that allows the apartment to reduce the contract to real world, including the system of an obligation to make processing and programming to control of the advertising platform.

%------------------------------------------------

\section{Risks}

The first social advance is a problem for control of the platform. However, it is pledge to the smart token. This may be limited to ensure that the purchaser is interested to the price . The structure of the basis for fiat our policies within the world. In addition, but also sell them. The latter for a service information for any companies of the development of the second. The project details of the token changer in the price of the standard proof that a blockchain industry.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem[Smith, 2017]{Smith:2017dg}
Smith, Clay (2017).
\newblock Using recurrent neural networks to generate ICO whitepaper nonsense.
\newblock {\em Github}, https://github.com/smithclay/char-embeddings-ml-engine.
 
\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}
